Status and Best Practices for Reproducible Research In Plant Pathology

### 2017-08-15 README.rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

---
title: "Reproducible Plant Pathology"
output: github_document
---

[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)

@@

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published.

@@

Adam H Sparks (adamhsparks@gmail.com)  
Emerson M Del Ponte (delponte@ufv.br)  
Zachary Foster (zacharyfoster1989@gmail.com)  
Niklaus J Grünwald (grunwaln@science.oregonstate.edu)

@@

```
git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
```

Once the download is complete, open the `Reproducible.Plant.Pathology.Rproj` in
RStudio to begin working with the package and compendium files.

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.

@@

    docker run -dp 8787:8787 phytopathology/Reproducible.Plant.Pathology

>>>>

---
title: "Reproducibility in Plant Pathology"
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology)

@@

For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/phytopathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/phytopathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.

@@

Adam H Sparks (adamhsparks@gmail.com)

Emerson M Del Ponte (delponte@ufv.br)

Zachary Foster (zacharyfoster1989@gmail.com)

Niklaus J Grünwald (grunwaln@science.oregonstate.edu)

@@

```
git clone https://github.com/phytopathology/Reproducibility_in_Plant_Pathology.git
```

Once the download is complete, open the `Reproducibility_in_Plant_Pathology.Rproj` in
RStudio to begin working with the package and compendium files.

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `Reproducibility_in_Plant_Pathology.Rproj` in RStudio.

@@

    docker run -dp 8787:8787 phytopathology/Reproducibility_in_Plant_Pathology

### 2017-08-15 inst/paper/Sparks_et_al-main_text.Rmd
Housekeeping items
- Change name where necessary to reflect renaming repository, which
reflects the title of the paper more accurately

- Spell checking in the package and Rmd files

- Update the _pkgdown_ site to follow the flatly theme that the HTML
document uses

- Update package name/title

- Remove packrat files, need to think about checkpoint?

- Cleanup .gitignore

A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used. A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a paywall. A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes. The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).

>>>>

A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used. A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall. A highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run more easily following download of data and codes. The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).
